---
title: "Predicting Initial Unemployment Insurance Claims Using Google Trends"
author: "Paul Goldsmith-Pinkham + Aaron Sojourner"
date: "4/1/2020"
output:
  html_document:
    df_print: paged
---

<style type="text/css">
.main-container {
  max-width: 800px;
  margin-left: auto;
  margin-right: auto;
}
</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# if (!require("devtools")) install.packages("devtools")
# devtools::install_github("paulgp/gtrendsR")

#install.packages("RApiDatetime")

library(gtrendsR)
library(tidyverse)
library(ggrepel)
library(RApiDatetime)
library(lubridate)
library(zoo)
library(knitr)
library(kableExtra)
library(readxl)
library(janitor)
library(RColorBrewer)
library(data.table)

lm_eqn = function(m) {

  l <- list(a = format(coef(m)[1], digits = 2),
      b = format(abs(coef(m)[2]), digits = 2),
      r2 = format(summary(m)$r.squared, digits = 3));


    eq <- substitute(~~italic(R)^2~"="~r2,l)
    eq <- substitute(~~italic(R)^2~"="~r2,l)    

  as.character(as.expression(eq));                 
}

pull_data = function(loc, time_window, panel=FALSE) {
  if (panel==TRUE) {
    geo = c("US-CA",loc)
    res_post = gtrends(keyword=c("file for unemployment"),  geo = geo, 
                       time = time_window, onlyInterest = TRUE)
    state_data = res_post$interest_over_time %>%
      mutate(hits = as.numeric(hits)) %>%
      mutate(hits = replace_na(hits, 0))
    cutoff = dim(res_post$interest_over_time)[1]/length(geo)
    CA_max = state_data %>% filter(row_number() <= cutoff) 
    ## We do the filter thing to drop the comparison state out. 
    state_data = state_data %>% filter(row_number() > cutoff) %>% 
      group_by(geo) %>% 
      mutate(max_geo = max(hits), 
             scale = max_geo / max(CA_max$hits),
             hits = scale*hits)
    return(list(state_data = state_data))
  }
  else {
    geo = loc
    res_post = gtrends(keyword=c("file for unemployment"),  geo = geo, 
                       time = time_window, onlyInterest = TRUE)
    state_data = res_post$interest_over_time %>%
      mutate(hits = as.numeric(hits))
    return(list(state_data = state_data))    
  }
}

```

```{r load-data2, cache=TRUE, results='hide', show=FALSE, include=FALSE}
#Create geography
# location_vec = tibble::enframe(name = NULL,c(state.abb, "DC")) %>% mutate(geo = "US") %>%   unite(location, geo, value, sep="-")
# 
# # Loop multiple times and average, following Seth's paper
# data_full = tibble()
# for (j in seq(1,1)) {
# panel_data = list()
# for (i in seq(1,length(location_vec$location),4)) {
#   if (i < 49) {
#     panel_data[[i]] = pull_data(loc = location_vec$location[i:(i+3)], time_window="2020-2-01 2020-3-28", panel=TRUE)
#   }
#   else {
#      panel_data[[i]] = pull_data(loc = location_vec$location[i:(i+2)], time_window="2020-2-01 2020-3-28", panel=TRUE)
#   }
#     # be polite
#     Sys.sleep(.2)
# }
# 
# panel_data_states = list()
# for (i in seq(1,length(panel_data))) {
#   panel_data_states[[i]] = panel_data[[i]]$state_data
# }
# 
# # Parse data
# data_states_short = bind_rows(panel_data_states) %>%
#   mutate(location = substr(geo, 4,6)) %>%
#   ungroup() %>%
#   select(location, hits, date) %>%
#   mutate(date = ymd(date)) %>%
#   group_by(location, date) %>%
#   arrange(location, date)
# 
# data_full = data_full %>% bind_rows(data_states_short)
# #Sys.sleep(60)
# }
# # 
# data_states_short = data_full %>% group_by(location, date) %>% summarize(hits = mean(hits))
# ## We do this b/c otherwise Google Trends API shuts us off  (already blocked for today)
# data_states_short %>% write_csv("data/data_states_2020_02_01_2020_03_30d.csv")
# 

data_states_short = read_csv("data/data_states_2020_02_01_2020_03_30d.csv") 
data_states_short_recent =  read_csv("data/trends_Mar30_2pm.csv", skip = 2) %>% 
  mutate(date = date(Time)) %>%  
  gather(state_dirty, val, -date, -Time) %>%
  separate(col = state_dirty, into = c(NA, "state_name"), sep = ":") %>%
  mutate(state_name = trimws(state_name),
         state_name = str_remove(state_name,"\\("),
         state_name = str_remove(state_name,"\\)")) %>%
  group_by(date, state_name) %>% 
  summarize(hits = max(val)) %>%
  mutate(state_name = case_when(startsWith(state_name, "California") ~ "California",
                                TRUE ~ state_name)) %>%
  group_by(state_name, date) %>% 
  summarize(hits = mean(hits)) %>%
  left_join(tibble(state_name = state.name, state = state.abb)) %>%
  mutate(state = replace_na(state, "DC"))
  
```

```{r load-ntl-data, include=FALSE, cache=TRUE}
national_trend =  pull_data(loc = c("US"), time_window="2020-2-01 2020-3-30", panel=TRUE)
national_trend = national_trend$state_data %>% filter(geo == "US")  %>% 
  mutate(location = "USA") %>%
  ungroup() %>%
  select(date, hits, location) %>% mutate(date = date(date))
national_trend_recent = read_csv("data/ntl_03220328.csv") %>% mutate(date = date(datetime)) %>%
  group_by(date) %>% summarize(hits = max(hits)) %>% mutate(location = "USA")
national_trend_combined = national_trend %>% mutate(date = date(date)) %>%
  filter(date >= ymd("2020-02-22")) %>%
  full_join(national_trend_recent %>% rename(hits2 = hits)) %>%
  group_by(location) %>%
  mutate(max_new =  case_when(date == ymd("2020-03-24") ~ hits2),
         max_new2 = max(max_new, na.rm=TRUE),
         max_old =  case_when(date == ymd("2020-03-24") ~ hits),
         max_old2 = max(max_old, na.rm=TRUE)) %>%
  mutate(hits3 = hits2 * max_old2/(max_new2)) %>% 
  mutate(hits = case_when(date > ymd("2020-03-24") ~ hits3,
                                      TRUE ~ hits)) %>% 
  select(date, hits, location) %>%
  ungroup()

data_states_short_combined = data_states_short %>% 
  filter(date >= ymd("2020-02-22")) %>%  
  full_join(data_states_short_recent %>% rename(hits2 = hits,
                                                location = state)) %>%
  group_by(location) %>%
  mutate(max_new =  case_when(date == ymd("2020-03-24") ~ hits2),
         max_new2 = max(max_new, na.rm=TRUE),
         max_old =  case_when(date == ymd("2020-03-24") ~ hits),
         max_old2 = max(max_old, na.rm=TRUE)) %>%
  mutate(hits3 = hits2 * max_old2/(max_new2)) %>% 
  mutate(hits = case_when(date > ymd("2020-03-24") ~ hits3,
                                      TRUE ~ hits)) %>% 
  select(-hits3, -hits2, -starts_with("max_old"), -starts_with("max_new"), -state_name) %>%
  ungroup()

#data_states_short = data_states_short_combined
```

```{r, include=FALSE, message=FALSE, warning=FALSE}
### Calculate growth rate in Google Measures
data_states_short = data_states_short %>% group_by(location) %>% 
  mutate( hits_ma = rollmean(x = hits, 7, align = "right", fill = NA))

weekly_data = data_states_short %>% mutate(dow = wday(date)) %>%
  mutate(week = epiweek(date)) %>% group_by(week, dow, location) %>% 
  summarize(hits = mean(hits, na.rm= TRUE), date = max(date)) %>% filter(month(date) > 1)
weekly_data2 = data_states_short %>% 
  mutate(week = epiweek(date)) %>% group_by(week, location) %>% 
  summarize(hits = mean(hits, na.rm= TRUE), date = max(date)) %>% filter(month(date) > 1)
weekly_data3 = data_states_short %>% bind_rows(national_trend) %>%
  mutate(week = epiweek(date)) %>% group_by(week, location) %>% 
  summarize(hits = mean(hits, na.rm= TRUE), date = max(date)) %>% filter(month(date) > 1)

growth_rate_weekly = weekly_data %>% 
   filter(week >= 8 & week < 14 ) %>%
  select(location, hits = hits, week, date, dow) %>%
  mutate(late = case_when(week == 12 ~ "late",
                          week == 13 ~ "late_nyt",
                          TRUE ~ "early")) %>%
  group_by(location, late, dow) %>%
  summarize(hits = mean(hits, na.rm=TRUE)) %>%
  filter(!is.na(hits)) %>% spread(late, hits) %>%
  mutate(rate = late/(early+1),
         diff = late - early)

growth_rate_weekly2 = weekly_data2 %>% group_by(location) %>% 
   filter(week >= 8 & week < 13) %>%
  select(location, hits = hits, week, date) %>%
  mutate(late = case_when(week == 12 ~ "late",
                          TRUE ~ "early")) %>%
  group_by(location, late) %>%
  summarize(hits = mean(hits, na.rm=TRUE)) %>%
  filter(!is.na(hits)) %>% spread(late, hits) %>%
  mutate(rate = late/(early+1),
         diff = late - early)

growth_rate_weekly3 = weekly_data3 %>% 
   filter(week >= 8 & week < 14 ) %>%
  select(location, hits = hits, week, date) %>%
  mutate(late = case_when(week == 12 ~ "late",
                          week == 13 ~ "late_nyt",
                          TRUE ~ "early")) %>%
  group_by(location, late) %>%
  summarize(hits = mean(hits, na.rm=TRUE)) %>%
  filter(!is.na(hits)) %>% spread(late, hits) %>%
  mutate(rate = late/(early+1),
         diff = late - early)

```

```{r, include=FALSE, message=FALSE, warning=FALSE}

## Load UI data
library(readxl)
UI_Claims_March21 <- read_excel("data/UI_Claims_March21.xlsx", skip = 1) %>% 
  filter(!is.na(State)) %>% select(location = State, ui_growth = GrowthFactor, baseline_ui = `2/22-3/14`)
UI_Claims_March28 <- read_excel("data/UI_Claims_March28.xlsx", sheet = "Weekly_Summary", col_names = FALSE, skip = 4) %>%
  select(location = ...1, baseline_ui =...2, proj_ui_lastwk = ...4, proj_ui_thiswk =...5) %>%
  filter(!is.na(location))  %>%
  mutate(baseline_ui = as.numeric(baseline_ui),
         proj_ui_lastwk = as.numeric(proj_ui_lastwk),
         proj_ui_thiswk = as.numeric(proj_ui_thiswk))

### Load in Daily UI Data

daily_UI_Claims = tibble()
for (i in c(state.abb,"DC")) {
  daily_UI_Claims = daily_UI_Claims %>% bind_rows(
    read_excel("data/UI_Claims_March28.xlsx", sheet = i) %>%
      select(date, ui_claims_daily = reported_claims...2) %>%
      mutate(location = i))
}

daily_UI_Claims = daily_UI_Claims %>% filter(!is.na(ui_claims_daily)) %>%
  mutate(date = date(date))

### Load in true State Data

UI_Claims_March21_True <- read_excel("data/UI_20200326_states.xlsx") %>%
  left_join(tibble(STATE = state.name, location = state.abb)) %>%
  mutate(location = replace_na(location, "DC")) %>%
  select(location, Advance)

UI_Claims_March28_True <- read_excel("data/StateUIClaims03282020.xlsx", sheet = "Sheet1") %>%
  left_join(tibble(STATE = state.name, location = state.abb)) %>%
  select(location, `2 week total`, advance_0322, advance_0315, updated_0315) %>%
  mutate(location = replace_na(location, "DC"))


## Read in Labor force data

lf_state <- read_excel("data/labor_force_state.xlsx", sheet = "Sheet1") %>%
  left_join(tibble(state = state.name, location = state.abb)) %>%
  mutate(location = replace_na(location, "DC")) %>%
  select(location, labor_force = lf_022020)

### Load in "report level" data
report_level_UI_data <- read_excel("data/report_level_UI_data_new.xlsx", 
                                                        sheet = "zs") %>%
  mutate(date_start = date(date_start),
         date_end = date(date_end),
         article_date = janitor::excel_numeric_to_date(as.numeric(article_date))
         )
  
report_level_UI_data <- report_level_UI_data %>% bind_rows(read_excel("data/report_level_UI_data_new.xlsx", 
                                                        sheet = "dp") %>%
  mutate(date_start = date(date_start),
         date_end = date(date_end),
         article_date = janitor::excel_numeric_to_date(as.numeric(article_date))
         ))

report_level_UI_data = report_level_UI_data %>% filter(!is.na(date_start) & !is.na(date_end)) %>% 
  select(location = state, date_start, date_end, claims) %>%
  group_by(location, date_start, date_end) %>%
  summarize(claims = mean(claims))

report_level_UI_data_fill = report_level_UI_data %>% group_by(location) %>% mutate(report_id = row_number()) %>%
  mutate(num_days =1 + date_end - date_start ) %>% 
  mutate(claims_avg = claims / as.numeric(num_days)) %>%
  select(-claims, -num_days) %>% 
  gather(date_, date, -location, -claims_avg, -report_id) %>% 
  select(-date_) %>% 
  arrange(location, report_id, date) %>% 
  group_by(location, report_id) %>% 
  complete(date = seq.Date(from = min(date), to = max(date), by="day"), claims_avg) %>%
  group_by(location, report_id, date) %>% 
  summarize(claims_avg = mean(claims_avg, na.rm=TRUE))

report_UI_GT_data = report_level_UI_data_fill %>% 
  left_join(data_states_short) %>% group_by(location, report_id) %>%
  summarize(claims = mean(claims_avg), hits = mean(hits), week_end = max(date), week_start = min(date)) %>% 
  left_join(growth_rate_weekly3 %>% select(location, early)) %>%
  mutate(hits_norm = hits - early) %>%
  left_join(UI_Claims_March21 %>% select(location, baseline_ui)) %>%
  mutate(ui_norm = claims / baseline_ui)

model_report_daily = lm(ui_norm ~ hits_norm, data =  report_UI_GT_data %>% 
         filter(epiweek(week_end) == 12), weight = baseline_ui)

```

```{r, include=FALSE, message=FALSE, warning=FALSE}

daily_plot_data = daily_UI_Claims %>% 
  left_join(data_states_short) %>%
  left_join(UI_Claims_March28 %>% select(baseline_ui, location) %>% 
              group_by(location) %>% filter(row_number() == n())) %>%
  mutate(dow = wday(date)) %>%
  left_join(growth_rate_weekly %>% select(location, dow, early)) %>%
  group_by(location) %>% mutate(hits_first = first(hits),
                                ui_first = first(ui_claims_daily)) %>%
  mutate(ui_norm = ui_claims_daily/baseline_ui,
         ui_index = ui_claims_daily/ui_first,
         hits_norm = (hits - early),
         hits_index = hits/(hits_first+1))

model_daily = lm(ui_norm ~ hits_norm, data =  daily_plot_data %>% 
         filter(epiweek(date) == 12), weight = baseline_ui)

daily_predict_data = data_states_short %>% 
  filter(epiweek(date) > 11 & epiweek(date) < 14) %>%
  mutate(dow = wday(date)) %>%
  left_join(growth_rate_weekly %>% 
              select(location, early, dow)) %>%
  left_join(UI_Claims_March28 %>% 
              select(baseline_ui, location) %>% 
              group_by(location) %>% 
              filter(row_number() == n())) %>%
  mutate(hits_norm = hits - early) %>%
  mutate(ui_claims_daily_hat = 
           baseline_ui*(
             ((hits_norm) * model_daily$coefficients[2]) + 
               model_daily$coefficients[1]),
         ui_claims_report_daily_hat = 
           baseline_ui*(
             ((hits_norm) * model_report_daily$coefficients[2]) + 
               model_report_daily$coefficients[1])
         ) %>%
  left_join(daily_plot_data %>% select(location, date, ui_claims_daily, hits_norm)) 


```



```{r, include=FALSE, message=FALSE, warning=FALSE}
se.fit = predict(model_daily, daily_predict_data %>% 
  mutate(week = epiweek(date)), se.fit = TRUE)$se.fit
se_report.fit = predict(model_report_daily, daily_predict_data %>% 
  mutate(week = epiweek(date)), se.fit = TRUE)$se.fit

weekly_predict_data = daily_predict_data %>% 
  mutate(week = epiweek(date))  %>%
  bind_cols(tibble(se = se.fit, se_report = se_report.fit)) %>%
  mutate(se = se * baseline_ui,
         se_report = se_report * baseline_ui) %>%
  left_join(report_level_UI_data_fill %>% group_by(location, date) %>% summarize(claims_avg = mean(claims_avg, na.rm = TRUE))) %>%
  mutate(combined_prediction = case_when(TRUE ~ ui_claims_daily_hat),
         combined_prediction_se = case_when(TRUE ~ se,
                                            #is.na(ui_claims_daily) ~ se,
                                         #TRUE ~ 0
                                         ),
         combined_prediction_report =  ui_claims_report_daily_hat,
         combined_prediction_se_report = se_report) %>%
  select(location, date, hits, hits_norm, ui_claims_daily_hat, ui_claims_daily, 
         combined_prediction, combined_prediction_se, 
         combined_prediction_report, combined_prediction_se_report, week) %>%
  group_by(location, week) %>%
  summarize(predicted_ui = sum(combined_prediction),
            predicted_ui_lb =  sum(combined_prediction) - 2*sum(combined_prediction_se),
            predicted_ui_ub =  sum(combined_prediction) + 2*sum(combined_prediction_se),
            predicted_ui_report = sum(combined_prediction_report),
            predicted_ui_lb_report =  sum(combined_prediction_report) - 2*sum(combined_prediction_se_report),
            predicted_ui_ub_report =  sum(combined_prediction_report) + 2*sum(combined_prediction_se_report),
            first_date = first(date),
            last_date = last(date))  



```


```{r, echo=FALSE, warning=FALSE, message=FALSE}


joined_data = growth_rate_weekly2  %>% left_join(UI_Claims_March21)  %>% filter(!is.na(rate)) %>%
  mutate(ui_growth = as.numeric(ui_growth),
         projected_init_claims_aaron = ui_growth*baseline_ui)

model_fit_diff = lm(ui_growth ~ diff, data = joined_data, na.action= na.exclude)
model_fit_diff_weighted = lm(ui_growth ~ diff, data = joined_data, 
                             na.action= na.exclude, weight = baseline_ui)

fitted_data = joined_data %>% 
  ungroup() %>%
  mutate(fitted = is.na(ui_growth),
         pred = model_fit_diff$coefficients[1] + model_fit_diff$coefficients[2]*diff,
         projected_init_claims = pred*baseline_ui,
         pred_weight = model_fit_diff_weighted$coefficients[1]+model_fit_diff_weighted$coefficients[2]*diff,
         projected_init_claims_weight = pred_weight*baseline_ui
  ) %>%
  ungroup() %>% 
  mutate(combined_projection = case_when(fitted == TRUE ~ projected_init_claims,
                                         TRUE ~ projected_init_claims_aaron
                                         ),
         combined_growth = case_when(fitted = TRUE ~ pred,
                                     TRUE ~ ui_growth),
         combined_projection_weight = case_when(fitted == TRUE ~ projected_init_claims_weight,
                                         TRUE ~ projected_init_claims_aaron
                                         ))
options(knitr.kable.NA = "--")
output2 = fitted_data %>% select(`State` = location, `UI Claims From News` = projected_init_claims_aaron, 
                       `Google Trends Change` = diff,
                       `Forecasted UI Claims` = combined_projection ) 

report_output_text = weekly_predict_data %>% 
  ungroup() %>% filter(week == 12 | week == 13) %>%
  mutate(predicted_ui = predicted_ui_report/1e6, 
         predicted_ui_lb = predicted_ui_lb_report/1e6,
         predicted_ui_ub = predicted_ui_ub_report/1e6) %>%
  mutate(predicted_ui_sa = case_when(week == 12 ~ predicted_ui/0.833,
                                     week == 13 ~ predicted_ui/0.876),
         predicted_ui_lb_sa = case_when(week == 12 ~ predicted_ui_lb/0.833,
                                     week == 13 ~ predicted_ui_lb/0.876),
         predicted_ui_ub_sa = case_when(week == 12 ~ predicted_ui_ub/0.833,
                                     week == 13 ~ predicted_ui_ub/0.876)) %>%
  select(week, predicted_ui, predicted_ui_lb, predicted_ui_ub,
         ends_with("sa")) %>%
  group_by(week) %>% summarize_all(sum) 
  

options(knitr.kable.NA = "--")
report_output = weekly_predict_data %>% ungroup() %>% filter(week == 12 | week == 13) %>%
  select(location, week, predicted_ui = predicted_ui_report) %>%
  spread(week, predicted_ui) %>%
  left_join(UI_Claims_March21_True) %>%
  left_join(growth_rate_weekly3) %>%
  rename(State = location) %>%
  left_join(output2) %>%
  mutate(google_12 = late - early,
         google_13 = late_nyt - early) %>%
  select(State, `UI Claims From News`, Advance, google_12, `12`,  google_13, `13`) %>% 
  mutate(Total = `12` + `13`)
```


*Note: Data+code for this are available here  https://docs.google.com/spreadsheets/d/1RN1XJLIpU12QUwMpkF0DNiV8fkeqdHbWHta2sRfEZT4/edit#gid=651560 and here https://github.com/paulgp/GoogleTrendsUINowcast *

**Many thanks to Dylan Piatt and Zach Swaziek for their help with this**

# Goal

Understanding changes in national and state-level initial unemployment insurance (UI) claims has value to markets, policymakers, and economists. Initial claims measure the number of Americans filing new claims for UI benefits is one of the most-sensitive, high-frequency official statistics used to detect changes in the labor market. However, official federal data on UI claims comes out at a weekly interval and at a lag. The U.S. Department of Labor aggregates reports state unemployment insurance systems for weekly release of advance estimates on Thursdays, which covers the prior Sunday to Saturday week. They revise it over the following week, so official estimates are released 12 days after each week ends. We aim to forecast official UI initial claims statistics. 

Below, we forecast initial claims nationally and by state for the week ending Saturday, March 28. The official, advance estimates will be released Thursday, April 2. While last week was a record-setting week, this week's UI numbers look poised to break that record again, with the largest rise in new unemployment claims in U.S. history, due to widespread quarantines. But just how large will this shock be?

Many state agencies reported partial information to the press over the course of the week, due the staggering growth in UI claims. The first part of our approach gathers and harmonizes the reported numbers across press reports to construct news report measures of UI claims in a state over a set of days. The Data section provides more details.
<!-- In many cases, this involves extrapolating to a weekly number based on a few days of reported information. Taking the ratio of this to the average number of initial claims over the four, prior weeks measures change in initial claims for the subset of states with any reports this week. -->

The second part of our approach imputes state's UI claims harnessing data from Google Trends. We construct a daily panel dataset of the intensity of search for the term "file for unemployment" for each state. We regress this measure on the set of day-states where we have constructed a growth rate in UI claims using news reports, and use this to impute the initial claims for all states. We do this by forecasting UI claims using the estimated daily model and the panel of Google trends data.

These models are new and only partially validated.  We always welcome feedback (asojourn@umn.edu).

# Summary of Results

For the week ending March 21, the model yields initial national UI claims (seasonally adjusted)   of `r round(report_output_text$predicted_ui_sa[1], digits = 1)`. Our confidence intervals range from `r round(report_output_text$predicted_ui_lb_sa[1], digits = 1)`	to `r round(report_output_text$predicted_ui_ub_sa[1], digits = 1)` million. Relative to the advance estimates from the state, this number is high. Further below, we discuss reasons for this, mainly related to seemingly low UI numbers from states which had had news reports suggesting much higher numbers. This discrepancy is likely due to overwhelmed UI offices in these states.

For the week of 3/22-3/28, we use the estimated relationship from 3/15-3/21 between Google Trends interest and UI claims to predict initial claims. Our model implies a prediction of `r round(report_output_text$predicted_ui_sa[2], digits = 1)` million UI claims, seasonally adjusted, with a 95\% CI of `r round(report_output_text$predicted_ui_lb_sa[2], digits = 1)` million and `r round(report_output_text$predicted_ui_ub_sa[2], digits = 1)` million for the week of 3/22-3/28.

```{r, echo=FALSE, warning=FALSE, message=FALSE}

weekly_predict_data  %>%  ungroup() %>% 
  mutate(week_str = case_when(week == 12 ~ "3/15-3/21",
                                      week == 13 ~ "3/22-3/28")) %>% 
  group_by(week_str) %>%
  mutate(predicted_ui_report = predicted_ui_report/1e6,
         predicted_ui_lb_report = predicted_ui_lb_report/1e6,
         predicted_ui_ub_report = predicted_ui_ub_report/1e6) %>% 
  mutate(predicted_ui_sa = case_when(week == 12 ~ predicted_ui_report/0.833,
                                     week == 13 ~ predicted_ui_report/0.876),
         predicted_ui_lb_sa = case_when(week == 12 ~ predicted_ui_lb_report/0.833,
                                     week == 13 ~ predicted_ui_lb_report/0.876),
         predicted_ui_ub_sa = case_when(week == 12 ~ predicted_ui_ub_report/0.833,
                                     week == 13 ~ predicted_ui_ub_report/0.876)) %>%
  select(week_str, ends_with("report"), ends_with("sa")) %>%
  summarize_all(sum) %>%
  kable(digits = 1, format.args = list(big.mark = ",", scientific = FALSE),
        col.names = c("Week", "Predicted UI Claims (millions)", 
                                  "Lower Bound",
                                  "Upper Bound",
                      "Predicted UI Claims (millions)", 
                                  "Lower Bound",
                                  "Upper Bound")) %>%
  kable_styling(bootstrap_options = c("striped", "hover"), full_width = F) %>%
  add_header_above(c(" " = 2, "95% Confidence Interval" = 2, " " = 1, "95% Confidence Interval" = 2)) %>%
  add_header_above(c(" " = 1, "Not Seasonally Adjusted" = 3, "Seasonally Adjusted" = 3))
```


We predict large variation across states and the table below describes, for each state, the estimated claims level based only on extrapolation from news reports, the Google Trends change and the forecast claims level based on the model combining news reports and Google Trends information. These state estimates are not seasonally adjusted.

```{r, echo = FALSE, warning=FALSE, message=FALSE}

report_output %>% left_join(UI_Claims_March28_True %>% rename(State = location)) %>% 
  mutate(`2 week total`  = advance_0322 + updated_0315) %>%
  select(State,
         google_12, advance_0315, updated_0315,
           `12`,  google_13, advance_0322,
         `13`,   `2 week total`,  Total ) %>%
  kable(digits = 0, format.args = list(big.mark = ",", scientific = FALSE), 
         col.names = c("State",  "Google Trends Change from 2/22-3/14", "Advance Official UI Claims", "Revised Official UI Claims",  "Predicted UI Claims", "Google Trends Change from 2/22-3/14",  "Advance Official UI Claims", "Predicted UI Claims", "Revised + Advance Official UI Claims", "Predicted UI Claims")) %>%
  kable_styling(bootstrap_options = c("striped", "hover"), full_width = F) %>%
  add_header_above(c(" " = 1, "Week 3/15-3/21" = 4, "Week 3/22-3/28" = 3, "Combined Weeks 3/15-3/28"=2)) %>%
  scroll_box(width = "1000px", height = "400px")

weekly_predict_data %>% ungroup() %>% filter(week == 12 | week == 13) %>%
  select(location, week, predicted_ui) %>%
  spread(week, predicted_ui) %>%
  left_join(UI_Claims_March21_True) %>%
  left_join(growth_rate_weekly3) %>%
  rename(State = location) %>%
  left_join(output2) %>%
  mutate(google_12 = late - early,
         google_13 = late_nyt - early) %>%
  select(State, `UI Claims From News`, Advance, google_12, `12`,  google_13, `13`) %>% 
  mutate(Total = `12` + `13`) %>% 
  select(State, pred_total = Total, pred_0315 = `12`, pred_0322 =`13`,) %>%
  write_csv("data/state_predictions_weekly03312020.csv")
```



# Data Sources

## News Sources

We are greatly helped by many states reporting various claims numbers over the course of the week. We gather and harmonize the various reported numbers across press reports to construct a dataset of news "reports". We found reports for all 50 states and the District of Columbia. See this website for the data: https://docs.google.com/spreadsheets/d/1RN1XJLIpU12QUwMpkF0DNiV8fkeqdHbWHta2sRfEZT4/edit#gid=651560

Reports tend to describe the number of claims for a given set of dates (from start date $S$ to end date $E$) based on information from state officials. Since reports vary over what periods that they report data (some report over a 4 day span, some over a one day span), we reconcile these differences by using a "report-level" dataset, wherein each report is treated as an observation. For that report, we construct the per-day average claim, and call that our claim measure $C$. For our estimation below, we then link this to the average of the daily Google Trends data for that particular spell.

## Google Trends

We pull data from http://www.google.com/trends, a Google product that aggregates search volume by geography. Many papers have used this previously as measures of activity -- one example is Stephens-Davidowitz (2014).

The data is unusually reported. To quote Google:

> Search results are normalized to the time and location of a query by the following process: Each data point is divided by the total searches of the geography and time range it represents to compare relative popularity. Otherwise, places with the most search volume would always be ranked highest. The resulting numbers are then scaled on a range of 0 to 100 based on a topic’s proportion to all searches on all topics.

More specifically, to quote Seth Stephens-Davidowitz:

> It (Google Trends) takes the percent of all searches that use that term; then divides by the highest number. So if 1 percent of searches include coronavirus in City A and 0.5 percent of searches include coronavirus in City B, city B will have a number half as high as City A. 

We pull a dataset of all fifty states (as well as Washington DC and the national trend ("USA")), collecting an index of the relative search volume for "file for unemployment." A crucial feature of the Google Trends API is it is only possible to compare five locations per search. To elide this issue, we pull data for California plus four states, and continuously renormalize each state by $\max{Index_{s}}/\max{Index_{CA}}$. This way, all states are relative to California (and now some of the index measures will be larger than 100.), and comparisons can be made both across time and geographies.

We pull data for all states, as well as the national trend, from February 1st to March 28th (the latest that the data is currently available). We plot the relative indices for select states below, and see that similar to the UI growth in our news data, there is also substantial differences across states in the growth of the search term. Additionally, the weekend effect is quite noticeable, with far more search activity on the Monday after a weekend and the Friday before. 


```{r, fig.height = 8, fig.width=10, echo=FALSE, warning=FALSE, message=FALSE}
gg_color_hue <- function(n) {
  hues = seq(15, 375, length=n+1)
  hcl(h=hues, l=65, c=100)[1:n]
}
state_labels = data_states_short %>% 
  arrange(location, date) %>%
  group_by(location) %>%
  filter(!is.na(hits)) %>%
  filter(row_number() == n()) 



plot_data_ntl = national_trend %>% mutate(date = date(date)) %>%
  filter(date >= ymd("2020-02-22") & date <= ymd("2020-03-29")) %>%
  mutate(location = "USA") %>%
  bind_rows(data_states_short %>% filter(date >= ymd("2020-02-22")) %>% 
              filter(location %in% c("NY", "CA", "OH", "PA", "MI", "FL", "IL")))

plot_data_ntl$location <- relevel(as.factor(plot_data_ntl$location), "USA")
dates = plot_data_ntl %>% select(date) %>% unique()
sats <- which( wday(dates$date)==7)
suns <- which(wday(dates$date)==1)

plot_data_ntl %>% write_csv("data/plot_data_ntl.csv")
ggplot() + 
  geom_line(data = plot_data_ntl, aes(y = hits, x = date(date), color= as.factor(location))) +
  scale_x_date(date_breaks = "7 days", date_labels = "%m-%d") +
  geom_text_repel(data = plot_data_ntl %>% group_by(location) %>% filter(row_number() == n()), 
                  aes(y = hits, x = date, label = location, color=location),
                  nudge_x = 1.5, show.legend=FALSE) +
  geom_rect(aes(xmin=dates$date[sats[1]], xmax=dates$date[suns[1]],
                  ymin=-Inf, ymax=Inf),
            fill='grey', alpha=0.25) +
  geom_rect(aes(xmin=dates$date[sats[2]], xmax=dates$date[suns[2]],
                  ymin=-Inf, ymax=Inf),
            fill='grey', alpha=0.25) +
  geom_rect(aes(xmin=dates$date[sats[3]], xmax=dates$date[suns[3]],
                  ymin=-Inf, ymax=Inf),
            fill='grey', alpha=0.25) +
  geom_rect(aes(xmin=dates$date[sats[4]], xmax=dates$date[suns[4]],
                  ymin=-Inf, ymax=Inf),
            fill='grey', alpha=0.25) +
  geom_rect(aes(xmin=dates$date[sats[5]], xmax=dates$date[suns[5]],
                  ymin=-Inf, ymax=Inf),
            fill='grey', alpha=0.25) +
    geom_rect(aes(xmin=dates$date[sats[6]], xmax=dates$date[suns[6]],
                  ymin=-Inf, ymax=Inf),
            fill='grey', alpha=0.25) +
  theme_classic(base_size=15) +
  scale_color_manual(values = c(  "black", gg_color_hue(7)))+
  labs(x = "Date",
       y = "",
       title="Daily Google search intensity  for 'File for unemployment'",
       subtitle = "From 2020-2-22 to 2020-3-28, highlighting national trend and select states",
       caption = "Weekends shaded",
       color = "Search Regions"
  ) 
ggsave("plot_data_ntl.pdf")
# 
# plot_data_ntl2 = national_trend_combined %>% mutate(date = date(date)) %>%
#   filter(date >= ymd("2020-02-22")) %>%
#   mutate(location = "USA") %>%
#   bind_rows(data_states_short_combined %>% filter(date >= ymd("2020-02-22"))) %>%
#   left_join(UI_Claims_March21 %>%   arrange(baseline_ui) %>% filter(row_number() > 7*n()/8)) %>%
#   filter(!is.na(baseline_ui) | location == "USA")
# 
# plot_data_ntl2$location = relevel(factor(plot_data_ntl2$location), "USA")
# 
# week_growth = plot_data_ntl2 %>% mutate(week = epiweek(date)) %>% 
#    mutate(late = case_when(week == 12 ~ "late",
#                           week == 13 ~ "late_nyt",
#                           TRUE ~ "early"))  %>%
#   group_by(late, location) %>%
#   summarize(hits = mean(hits)) %>%
#   select(hits, location, late) %>%
#   spread(late, hits) %>% 
#   mutate(diff = (late_nyt -late) )
# # 
# ggplot() +
#   geom_col(data = week_growth, aes(y = diff, x = reorder(location,-diff)), fill = "blue") +
#   coord_flip() +
#   theme_classic(base_size=15) +
#   labs(x = "States",
#        y = "Change from 3/15-3/21 to 3/22-3/28",
#        title="Change in  Google search intensity  for 'File for unemployment'"
#   )
# 
# ggplot() +
#   geom_text(data = growth_rate_weekly3, aes(y = late_nyt, x = late, label=location)) +
#   geom_text(data = growth_rate_weekly3 %>% filter(location == "USA"), aes(y = late_nyt, x = late, label=location), color = "red") +
#   theme_classic(base_size=15) +
#   labs(x = "Search Intensity on 3/15-3/21",
#        y = "Search Intensity on 3/22-3/28",
#        title="Change in Google search intensity for 'File for unemployment'"
#   ) +
#   geom_abline(slope=1, intercept=0)  +
#   xlim(c(0,NA)) + ylim(c(0,NA))
# ggsave("rel_search_intensity.pdf")
growth_rate_weekly3 %>% select(location, early, late, late_nyt) %>%
  rename(baseline = early, week0315 = late, week0322 = late_nyt) %>% write_csv("growth_rate_weekly.csv")

# ggplot() + 
#   geom_text(data = week_growth, aes(y = late, x = early, label=location)) + 
#   geom_text(data = week_growth %>% filter(location == "USA"), aes(y = late, x = early, label=location), color = "red") + 
#   theme_classic(base_size=15) +
#   labs(y = "Search Intensity on 3/15-3/21",
#        x = "Search Intensity in 4 weeks prior",
#        title="Change in  Google search intensity  for 'File for unemployment'"
#   ) +
#   geom_abline(slope=1, intercept=0)  +
#   xlim(c(0,NA)) + ylim(c(0,NA))
# 
# ggplot() + 
#   geom_text(data = week_growth, aes(y = late_nyt, x = early, label=location)) + 
#   geom_text(data = week_growth %>% filter(location == "USA"), aes(y = late_nyt, x = late, label=location), color = "red") + 
#   theme_classic(base_size=15) +
#   labs(x = "Search Intensity in 4 weeks prior",
#        y = "Search Intensity on 3/22-3/28",
#        title="Change in  Google search intensity  for 'File for unemployment'"
#   ) +
#   geom_abline(slope=1, intercept=0)  +
#   xlim(c(0,NA)) + ylim(c(0,NA))
# 
# 
# ggplot() + 
#   geom_line(data = plot_data_ntl2 %>% filter(date < ymd("2020-03-29")), aes(y = hits, x = date(date), color= as.factor(location))) +
#   scale_x_date(date_breaks = "7 days", date_labels = "%m-%d") +
#   geom_text_repel(data = plot_data_ntl2 %>% filter(date < ymd("2020-03-29")) %>% group_by(location) %>% filter(row_number() == n()), 
#                   aes(y = hits, x = date, label = location, color=location),
#                   nudge_x = 1.5, show.legend=FALSE) +
#   geom_rect(aes(xmin=dates$date[sats[1]], xmax=dates$date[suns[1]],
#                   ymin=-Inf, ymax=Inf),
#             fill='grey', alpha=0.25) +
#   geom_rect(aes(xmin=dates$date[sats[2]], xmax=dates$date[suns[2]],
#                   ymin=-Inf, ymax=Inf),
#             fill='grey', alpha=0.25) +
#   geom_rect(aes(xmin=dates$date[sats[3]], xmax=dates$date[suns[3]],
#                   ymin=-Inf, ymax=Inf),
#             fill='grey', alpha=0.25) +
#   geom_rect(aes(xmin=dates$date[sats[4]], xmax=dates$date[suns[4]],
#                   ymin=-Inf, ymax=Inf),
#             fill='grey', alpha=0.25) +
#   geom_rect(aes(xmin=dates$date[sats[5]], xmax=dates$date[suns[5]],
#                   ymin=-Inf, ymax=Inf),
#             fill='grey', alpha=0.25) +
#     geom_rect(aes(xmin=dates$date[sats[6]], xmax=dates$date[suns[6]],
#                   ymin=-Inf, ymax=Inf),
#             fill='grey', alpha=0.25) +
#   theme_classic(base_size=15) +
#   scale_color_manual(values = c( "black", gg_color_hue(7)))+
#   labs(x = "Date",
#        y = "",
#        title="Daily Google search intensity  for 'File for unemployment'",
#        subtitle = "From 2020-2-22 to 2020-3-28, highlighting national trend and select states",
#        caption = "Weekends shaded",
#        color = "Search Regions"
#   ) 


# regions <- read_excel("data/regions.xlsx")
# plot_data = data_states_short %>% filter(date >= ymd("2020-02-22")) %>%
#               left_join(regions) %>%
#   group_by(location) %>% mutate(hits_lastday = case_when(row_number() ==n()-1 ~ hits)) %>%
#   group_by(bigregion) %>% mutate(max_index = max(hits, na.rm=TRUE),
#                               min_index = min(hits_lastday, na.rm=TRUE)) %>%
#   group_by(location) %>%
#   mutate(highlight_state = case_when(max_index == hits | (min_index == hits & row_number() == n()-1) | 
#                                        ((location == "OH" | location == "CA") & row_number() == n()) ~ 1)) %>%
#   mutate(highlight_state2 = max(highlight_state, na.rm=TRUE))

# ggplot() + 
#   geom_line(data = plot_data,
#             aes(y = hits, x = date, group= location), alpha = 0.3, show = FALSE) +
#     geom_line(data = plot_data %>% filter(highlight_state2 ==1),
#             aes(y = hits, x = date, color = as.factor(location)), show = FALSE) +
#   scale_x_date(date_breaks = "14 days", date_labels = "%m-%d") +
#   theme_classic(base_size=15) +
#   theme(
#   strip.background = element_blank(),
#   #strip.text.x = element_blank()
#   strip.text = element_text(size=10)
#   ) +
#   geom_text_repel(data = plot_data %>% filter(highlight_state == 1), 
#                   aes(y = hits, x = date, label = location),
#                   nudge_x = 1.5, show.legend=FALSE) +
#   facet_wrap(~bigregion) +
#   labs(x = "Date",
#        y = "",
#        title="Daily Google search intensity, by state, for 'File for unemployment'",
#        subtitle = "From 2020-2-22 to 2020-3-20, highlighting select states",
#   ) +
#   geom_hline(yintercept = 0, linetype=3)
```


# Estimation
Finally, we consider the relationship between these two measures. For the purposes of estimation, we focus on estimating only using reports that ended by 3/21. That way we are able to use the reports in the week of 3/22-3/28 as validation for our empirical model, as we discuss at the end.

With the claims reports as data points, we construct a growth measure, relative to each state’s the average of initial claims in the four prior weeks, ending Saturdays 2/22-3/14. We consider the change in the Google Trends index between the most recent week (3/15-3/21) and the day of the week average from the last four weeks (2/22-3/14). We then plot these two measures to consider how correlated the change in Google Trends search intensity is with UI growth.

```{r, fig.height = 8, echo=FALSE, warning=FALSE, message=FALSE}

  
# ggplot(data = daily_plot_data %>% filter(epiweek(date) > 11) %>%
#          mutate(week_str = case_when(epiweek(date) == 12 ~ "3/15-3/21",
#                                      epiweek(date) == 13 ~ "3/22-3/28")) %>%
#          filter(!is.na(hits))) +
#   geom_point(aes(y = ui_claims_daily/baseline_ui, x = hits - early,
#                  size = baseline_ui, color = as.factor(week_str))) +
#   geom_smooth(aes(y = ui_claims_daily/baseline_ui, x = hits - early, weight = baseline_ui), method = "lm") +
#   theme_classic(base_size=15) +
#   theme(
#   strip.background = element_blank(),
#   #strip.text.x = element_blank()
#   strip.text = element_text(size=10)
#   ) +
#   labs(x = "Google Search Intensity",
#        y = "Growth in UI Filings relative to Baseline",
#        title="Comparing daily Google search intensity for 'File for unemployment' vs. UI Claims",
#        subtitle = "From 2020-3-15 to 2020-3-23, for reporting states. Index normalizes by baseline period.",
#        size = "Baseline UI Claims",
#        color = "UI Reporting Week"
#   )

ggplot(data = report_UI_GT_data %>% 
         filter(epiweek(week_start) > 11 & epiweek(week_end) <= 12) %>%
         filter(!is.na(hits)) %>%
         mutate(num_days = 1 + as.numeric(week_end - week_start)) %>%
         mutate(high_freq = num_days < 3)) +
  geom_point(aes(y = ui_norm, x = hits_norm,
                 size = baseline_ui)) +
  geom_smooth(aes(y = ui_norm, x = hits_norm, weight = baseline_ui), method = "lm") +
  theme_classic(base_size=15) +
  theme(
  strip.background = element_blank(),
  #strip.text.x = element_blank()
  strip.text = element_text(size=10)
  ) +
  labs(x = "Change in Google Search Intensity",
       y = "Growth in UI Filings",
       title="Daily Google search intensity vs. UI Claims",
       subtitle = "From 2020-3-15 to 2020-3-22",
       caption = "Growth in UI claims from news reports",
       size = "Baseline UI Claims",
       color = "UI Reporting Week"
  )
```

```{r, echo=FALSE, warning=FALSE}
a = summary(model_report_daily, robust=TRUE)
a

```

We find a strong relationship between the two variables, with an adjusted $R^{2}$ of `r round(a$adj.r.squared, digits = 4)` when we weight observations by the states' baseline UI claims.  We use this estimated model and observed Google Trends changes to predict unemployment claims for the states lacking news-based estimates.

```{r, echo=FALSE, warning=FALSE, message=FALSE}

ggplot(data = daily_predict_data %>% filter(!is.na(ui_claims_daily)) ) +
  geom_point(aes(y = ui_claims_report_daily_hat/baseline_ui, x = hits - early, 
                 size = baseline_ui, color = "Predicted Growth in UI")) +
  geom_point(aes(y = ui_claims_daily/baseline_ui, 
                 x = hits - early, size = baseline_ui,  
                 color = "Actual Growth in UI")) +
  theme_classic(base_size=15) +
  theme(
  strip.background = element_blank(),
  #strip.text.x = element_blank()
  strip.text = element_text(size=10)
  ) +
  labs(x = "Change in Google Search Intensity",
       y = "Growth in UI Filings",
       title="Daily Google search intensity vs. UI Claims",
       subtitle = "From 2020-3-15 to 2020-3-22",
       caption = "Growth in UI claims from news reports",
       size = "Baseline UI Claims",
       color = "Actual vs. Fitted"
  )

```

Finally, we want to forecast the single statistic of weekly national initial claims. We do this in a very simple way, predicting the level of UI growth based on our model and the daily Google trends data, and then converting in UI claims numbers. We then sum up these predicted measures across states for each week. For the seasonally adjusted numbers, we then scale up 3/15-3/21 by 0.833, and 3/22-3/28 by 0.876.

For the week of 3/15-3/21, we predicted `r round(report_output_text$predicted_ui_sa[1], digits = 1)` million UI claims, with a 95\% CI of `r round(report_output_text$predicted_ui_lb_sa[1], digits = 1)` million and `r round(report_output_text$predicted_ui_ub_sa[1], digits = 1)` million for the week of 3/15-3/21.

For the week of 3/22-3/28, the figure of Google Trends interest above shows that Sunday, March 22, the first day that will be included in the report, was 500 percent higher than the prior Sunday and Monday 250 percent higher than the prior Monday. Google Trends interest continues to be high throughout the week, suggesting that there is significant UI activity. Combining this information with our model implies a prediction of `r round(report_output_text$predicted_ui_sa[2], digits = 1)` million UI claims, with a 95\% CI of `r round(report_output_text$predicted_ui_lb_sa[2], digits = 1)` million and `r round(report_output_text$predicted_ui_ub_sa[2], digits = 1)` million for the week of 3/22-3/28. 

We additionally report the non-seasonally adjusted numbers below as well.


```{r, echo=FALSE, warning=FALSE, message=FALSE}

weekly_predict_data  %>%  ungroup() %>% 
  mutate(week_str = case_when(week == 12 ~ "3/15-3/21",
                                      week == 13 ~ "3/22-3/28")) %>% 
  group_by(week_str) %>%
  mutate(predicted_ui_report = predicted_ui_report/1e6,
         predicted_ui_lb_report = predicted_ui_lb_report/1e6,
         predicted_ui_ub_report = predicted_ui_ub_report/1e6) %>% 
  mutate(predicted_ui_sa = case_when(week == 12 ~ predicted_ui_report/0.833,
                                     week == 13 ~ predicted_ui_report/0.876),
         predicted_ui_lb_sa = case_when(week == 12 ~ predicted_ui_lb_report/0.833,
                                     week == 13 ~ predicted_ui_lb_report/0.876),
         predicted_ui_ub_sa = case_when(week == 12 ~ predicted_ui_ub_report/0.833,
                                     week == 13 ~ predicted_ui_ub_report/0.876)) %>%
  select(week_str, ends_with("report"), ends_with("sa")) %>%
  summarize_all(sum) %>%
  kable(digits = 1, format.args = list(big.mark = ",", scientific = FALSE),
        col.names = c("Week", "Predicted UI Claims (millions)", 
                                  "Lower Bound",
                                  "Upper Bound",
                      "Predicted UI Claims (millions)", 
                                  "Lower Bound",
                                  "Upper Bound")) %>%
  kable_styling(bootstrap_options = c("striped", "hover"), full_width = F) %>%
  add_header_above(c(" " = 2, "95% Confidence Interval" = 2, " " = 1, "95% Confidence Interval" = 2)) %>%
  add_header_above(c(" " = 1, "Not Seasonally Adjusted" = 3, "Seasonally Adjusted" = 3))
```

# Model evaluation / validation

Based on the advance reports from the states, we can evaluate how we did in our forecasts. We're able to do this in two ways -- comparing our estimates to the advance estimates, and using a hold-out sample.

## The Week of 3/15-3/21

For the week of 3/15-3/21, there are initial advance reports of UI claims at the state level that reported on March 26. We compare the model's predictions for that week relative to the advance numbers, and find that for many states the model did quite well. However, for certain states, particularly California and New York, it was substantially over. This discrepancy may be due to overwhelm of  UI administrative systems in those states.

```{r, echo=FALSE, message=FALSE, warning=FALSE}
evaluation = weekly_predict_data %>% ungroup() %>% 
  filter(week == 12) %>%
  select(-week) %>%
  left_join(UI_Claims_March21_True) %>%
  select(`State` = location,
         Advance,
         `Predicted UI Claims` = predicted_ui_report, 
         `Lower Bound`=predicted_ui_lb,
         `Upper Bound`=predicted_ui_ub) %>% 
  left_join(output2)  %>%
  select(State, `UI Claims From News`, `Google Trends Change`, Advance, `Predicted UI Claims`, `Forecasted UI Claims`) 

ggplot(data = evaluation) +
  geom_text(aes(x = Advance/1000, y = `Predicted UI Claims`/1000, label=State)) +
  labs(x = "Advance Official Estimates (thousands)",
       y = "Predicted Estimate of UI Claim (thousands)",
       title = "Comparing Model Predictions to Advance Estimates",
       subtitle = "Time Period:  3/15-3/21",
       color = "Prediction") +
  theme_classic(base_size=15) +
  annotate("text", x = -Inf, y = Inf, hjust = 0, vjust = 1,
           label = lm_eqn(lm(`Predicted UI Claims` ~ Advance, evaluation)), parse = TRUE)+
  geom_abline(slope=1, intercept=0)

ggplot(data = evaluation) +
  geom_text(aes(x = Advance/1000, y = `Predicted UI Claims`/1000, label=State))  +
  labs(x = "Advance Official Estimates (thousands)",
       y = "Predicted Estimate of UI Claim (thousands)",
       title = "Comparing Model Predictions to Advance Estimates",
       subtitle = "Time Period:  3/15-3/21",
       color = "Prediction") +
  theme_classic(base_size=15) +
    annotate("text", x = 3, y = 300, hjust = 0, vjust = 1,
           label = lm_eqn(lm(log(`Predicted UI Claims`) ~ log(Advance), evaluation)), parse = TRUE)+
  scale_y_log10() +
  scale_x_log10() +
  geom_abline(slope=1, intercept=0)



```

We can also look at the *revised* numbers reported on April 2nd and see how we do relative to those:


```{r, echo=FALSE, message=FALSE, warning=FALSE}
evaluation = weekly_predict_data %>% ungroup() %>% 
  filter(week == 12) %>%
  select(-week) %>%
  left_join(UI_Claims_March28_True) %>%
  select(`State` = location,
         Advance = updated_0315,
         `Predicted UI Claims` = predicted_ui_report, 
         `Lower Bound`=predicted_ui_lb,
         `Upper Bound`=predicted_ui_ub) %>% 
  left_join(output2)  %>%
  select(State, `UI Claims From News`, `Google Trends Change`, Advance, `Predicted UI Claims`, `Forecasted UI Claims`) 

ggplot(data = evaluation) +
  geom_text(aes(x = Advance/1000, y = `Predicted UI Claims`/1000, label=State)) +
  labs(x = "Updated Official Estimates (thousands)",
       y = "Predicted Estimate of UI Claim (thousands)",
       title = "Comparing Model Predictions to Updated Estimates",
       subtitle = "Time Period:  3/15-3/21, reported 4/2",
       color = "Prediction") +
  theme_classic(base_size=15) +
    annotate("text", x = -Inf, y = Inf, hjust = 0, vjust = 1,
           label = lm_eqn(lm(`Predicted UI Claims` ~ Advance, evaluation)), parse = TRUE)+
  geom_abline(slope=1, intercept=0)

ggplot(data = evaluation) +
  geom_text(aes(x = Advance/1000, y = `Predicted UI Claims`/1000, label=State))  +
  labs(x = "Updated Official Estimates (thousands)",
       y = "Predicted Estimate of UI Claim (thousands)",
       title = "Comparing Model Predictions to Updated Estimates",
       subtitle = "Time Period:  3/15-3/21, reported 4/2",
       color = "Prediction") +
  theme_classic(base_size=15) +
    annotate("text", x = 3, y = 300, hjust = 0, vjust = 1,
           label = lm_eqn(lm(log(`Predicted UI Claims`) ~ log(Advance), evaluation)), parse = TRUE)+
  scale_y_log10() +
  scale_x_log10() +
  geom_abline(slope=1, intercept=0)



```

## The Week of 3/22-3/28

Since we only use the week of 3/15-3/21 to estimate the model, we can also use the news reports from 3/22-3/28 to assess how well the model does. This is our leave-out sample, and hence will give us a sense of how stable the relationship is. 

```{r, echo=FALSE, warning=FALSE, message=FALSE}

## Validate with new report data in week 13/14
validation_data = daily_predict_data %>% 
  select(location, date, ui_claims_report_daily_hat) %>% 
  inner_join(report_level_UI_data_fill) %>%
  filter(week(date) >12) %>%
  group_by(report_id, location) %>%
  summarize(ui_claims_report_daily_hat = sum(ui_claims_report_daily_hat, 
                                             na.rm = TRUE),
            claims = sum(claims_avg, na.rm = TRUE),
            num_days = n()) %>%
  inner_join(UI_Claims_March21 %>% select(location, baseline_ui)) %>%
  mutate(claims_norm = claims / baseline_ui, y_hat_norm = ui_claims_report_daily_hat / baseline_ui)
ggplot(data = validation_data) +
  geom_text(aes(x = claims/1000, y=ui_claims_report_daily_hat/1000, label = location)) +
  geom_abline(slope = 1, intercept = 0) +
    labs(x = "News Report Estimates (thousands)",
       y = "Predicted Estimate of UI Claim (thousands)",
       title = "Comparing Model Predictions to News Estimates",
       subtitle = "Time Period:  3/22-3/28",
       color = "Num. days in report") +
  theme_classic(base_size=15) +
    annotate("text", x = -Inf, y = Inf, hjust = 0, vjust = 1,
           label = lm_eqn(lm(`Predicted UI Claims` ~ Advance, evaluation)), parse = TRUE)+
  # scale_y_log10() +
  # scale_x_log10() +
  geom_abline(slope=1, intercept=0)

a = summary(lm(data = validation_data, claims_norm ~ y_hat_norm),  robust=TRUE)
b = summary(lm(data = validation_data, claims_norm ~ y_hat_norm, weight = baseline_ui), robust=TRUE)

```
The model does remarkably well, with an adjusted $R^{2}$ of `r round(b$adj.r.squared, digits = 1)`.


The model does remarkably well, with an adjusted $R^{2}$ of `r round(b$adj.r.squared, digits = 4)`.

We can now also check how we did by comparing to advance estimates:

```{r, echo=FALSE, message=FALSE, warning=FALSE}
evaluation = weekly_predict_data %>% ungroup() %>% 
  filter(week == 13) %>%
  select(-week) %>%
  left_join(UI_Claims_March28_True) %>%
  select(`State` = location,
         Advance = advance_0322,
         `Predicted UI Claims` = predicted_ui_report, 
         `Lower Bound`=predicted_ui_lb,
         `Upper Bound`=predicted_ui_ub) %>% 
  left_join(output2)  %>%
  select(State, `UI Claims From News`, `Google Trends Change`, Advance, `Predicted UI Claims`, `Forecasted UI Claims`) 


ggplot(data = evaluation) +
  geom_text(aes(x = Advance/1000, y = `Predicted UI Claims`/1000, label=State)) +
  labs(x = "Advance Official Estimates (thousands)",
       y = "Predicted Estimate of UI Claim (thousands)",
       title = "Comparing Model Predictions to Advance Estimates",
       subtitle = "Time Period:  3/22-3/28",
       color = "Prediction") +
  theme_classic(base_size=15) +
    annotate("text", x = -Inf, y = Inf, hjust = 0, vjust = 1,
           label = lm_eqn(lm(`Predicted UI Claims` ~ Advance, evaluation)), parse = TRUE)+
  geom_abline(slope=1, intercept=0)

ggplot(data = evaluation) +
  geom_text(aes(x = Advance/1000, y = `Predicted UI Claims`/1000, label=State))  +
  labs(x = "Advance Official Estimates (thousands)",
       y = "Predicted Estimate of UI Claim (thousands)",
       title = "Comparing Model Predictions to Advance Estimates",
       subtitle = "Time Period:  3/22-3/28",
       color = "Prediction") +
  theme_classic(base_size=15) +
    annotate("text", x = 3, y = 500, hjust = 0, vjust = 1,
           label = lm_eqn(lm(log(`Predicted UI Claims`) ~ log(Advance), evaluation)), parse = TRUE)+
  scale_y_log10() +
  scale_x_log10() +
  geom_abline(slope=1, intercept=0)



```


## Combining the two weeks

Finally, to avoid the congestion concerns, we can consider how we did at predicting the sum of the advance estimates, i.e. the total of the two sets of advance estimates between 3/15-3/28.

```{r, echo=FALSE, message=FALSE, warning=FALSE}
evaluation = weekly_predict_data %>% group_by(location) %>% 
  summarize(predicted_ui_report = sum(predicted_ui_report)) %>%
  left_join(UI_Claims_March28_True) %>%
  left_join(lf_state) %>%
  mutate(advance_sum = (advance_0322 + advance_0315)) %>%
  select(`State` = location,
         Advance = advance_sum,
         `Predicted UI Claims` = predicted_ui_report) %>% 
  left_join(output2)  %>%
  select(State, `UI Claims From News`, `Google Trends Change`, Advance, `Predicted UI Claims`, `Forecasted UI Claims`) 

model_graph = summary(lm(data = evaluation, Advance ~ `Predicted UI Claims`))
ggplot(data = evaluation) +
  geom_text(aes(x = Advance/1000, y = `Predicted UI Claims`/1000, label=State)) +
  labs(x = "Advance Official Estimates (thousands)",
       y = "Predicted Estimate of UI Claim s(thousands)",
       title = "Comparing Model Predictions to Advance Estimates",
       subtitle = "Time Period:  3/15-3/28",
       color = "Prediction") +
    annotate("text", x = -Inf, y = Inf, hjust = 0, vjust = 1,
           label = lm_eqn(lm(`Predicted UI Claims` ~ Advance, evaluation)), parse = TRUE)+
  theme_classic(base_size=15) +
  geom_abline(slope=1, intercept=0)

ggplot(data = evaluation) +
  geom_text(aes(x = Advance/1000, y = `Predicted UI Claims`/1000, label=State))  +
  labs(x = "Advance Official Estimates (thousands)",
       y = "Predicted Estimate of UI Claim (thousands)",
       title = "Comparing Model Predictions to Advance Estimates",
       subtitle = "Time Period:  3/15-3/28",
       color = "Prediction") +
  annotate("text", x = 10, y = 1000, hjust = 0, vjust = 1,
           label = lm_eqn(lm(log(`Predicted UI Claims`) ~ log(Advance), evaluation)), parse = TRUE)+
  theme_classic(base_size=15) +
  scale_y_log10() +
  scale_x_log10() +
  geom_abline(slope=1, intercept=0)

```

and scaled by labor force as of February 2020:

```{r, echo=FALSE, message=FALSE, warning=FALSE}
evaluation = weekly_predict_data %>% group_by(location) %>% 
  summarize(predicted_ui_report = sum(predicted_ui_report)) %>%
  left_join(UI_Claims_March28_True) %>%
  left_join(lf_state) %>%
  mutate(advance_sum = (advance_0322 + advance_0315)/labor_force,
         predicted_ui_report = predicted_ui_report/labor_force) %>%
  select(`State` = location,
         Advance = advance_sum,
         `Predicted UI Claims` = predicted_ui_report, labor_force) %>% 
  left_join(output2)  %>%
  select(State, `UI Claims From News`, `Google Trends Change`, Advance, `Predicted UI Claims`, `Forecasted UI Claims`, labor_force) 

model_graph = summary(lm(data = evaluation, Advance ~ `Predicted UI Claims`))
ggplot(data = evaluation) +
  geom_text(aes(x = Advance, y = `Predicted UI Claims`, label=State)) +
  labs(x = "UI Claims as share of Feb 2020 Labor Force",
       y = "Predicted Estimate as share of Feb 2020 Labor Force",
       title = "Comparing Model Predictions to Advance Estimates",
       subtitle = "Time Period:  3/15-3/28",
       color = "Prediction") +
  annotate("text", x = -Inf, y = Inf, hjust = 0, vjust = 1,
           label = lm_eqn(lm(`Predicted UI Claims` ~ Advance, evaluation, weight=labor_force)), parse = TRUE)+
  theme_classic(base_size=15) +
  geom_abline(slope=1, intercept=0)

```


As a check, comparing to the advance + revised:

```{r, echo=FALSE, message=FALSE, warning=FALSE}
evaluation = weekly_predict_data %>% group_by(location) %>% 
  summarize(predicted_ui_report = sum(predicted_ui_report)) %>%
  left_join(UI_Claims_March28_True) %>%
  select(State, `UI Claims From News`, `Google Trends Change`, Advance, `Predicted UI Claims`, `Forecasted UI Claims`) 

ggplot(data = evaluation) +
  geom_text(aes(x = Advance/1000, y = `Predicted UI Claims`/1000, label=State)) +
  labs(x = "Advance + Revised Official Estimates (thousands)",
       y = "Predicted Estimate of UI Claim s(thousands)",
       title = "Comparing Model Predictions to Advance + Revised Estimates",
       subtitle = "Time Period:  3/15-3/28",
       color = "Prediction") +
    annotate("text", x = -Inf, y = Inf, hjust = 0, vjust = 1,
           label = lm_eqn(lm(`Predicted UI Claims` ~ Advance, evaluation)), parse = TRUE)+
  theme_classic(base_size=15) +
  geom_abline(slope=1, intercept=0)

ggplot(data = evaluation) +
  geom_text(aes(x = Advance/1000, y = `Predicted UI Claims`/1000, label=State))  +
  labs(x = "Advance Official Estimates (thousands)",
       y = "Predicted Estimate of UI Claim (thousands)",
       title = "Comparing Model Predictions to Advance Estimates",
       subtitle = "Time Period:  3/15-3/28",
       color = "Prediction") +
  theme_classic(base_size=15) +
    annotate("text", x = 10, y = 1000, hjust = 0, vjust = 1,
           label = lm_eqn(lm(log(`Predicted UI Claims`) ~ log(Advance), evaluation)), parse = TRUE)+
  scale_y_log10() +
  scale_x_log10() +
  geom_abline(slope=1, intercept=0)

```

```{r, echo=FALSE, warning=FALSE, message=FALSE}

###### Liz doing state policy stuff #######

data_policy_states = read_xlsx("data/covid_closures_by_state.xlsx") 

data_policy_states <- mutate_at(data_policy_states, c("partial", "school", "complete"), funs(ymd)) %>%
  mutate(complete_week = epiweek(complete), partial_week = epiweek(partial), school_week = epiweek(school)) %>%
  mutate(complete_day = day(complete), partial_day = day(partial), school_day = day(school)) %>%
  mutate(region = tolower(state))

states <- map_data("state")

dates_map <- left_join(states, data_policy_states, by = "region")

#Map of complete closure orders

dates_map$complete <- format(dates_map$complete, format = "%m/%d")
complete_map <- 
  ggplot(dates_map, aes(long, lat, group = group)) + 
  geom_polygon(aes(fill = factor(complete)), color = "white") + 
  ggtitle("Non-Essential Business Closure Orders") +
  scale_fill_manual(values = colorRampPalette(brewer.pal(13, "GnBu"))(13), name = "Effective Date", na.value = "grey50", guide = "legend", drop = "TRUE") +
  theme(axis.text.x = element_blank(),
        axis.text.y = element_blank(),
        axis.ticks = element_blank(),
        rect = element_blank(),
        axis.title.y=element_blank(), 
        axis.title.x=element_blank()) 

#Map of partial closure orders

dates_map$partial <- format(dates_map$partial, format = "%m/%d")
takeout_map <- 
  ggplot(dates_map, aes(long, lat, group = group)) + 
  geom_polygon(aes(fill = factor(partial)), color = "white") + 
  ggtitle("Prohibition on Dining In and Partial Closure Orders") +
  scale_fill_manual(values = colorRampPalette(brewer.pal(13, "BuPu"))(13), name = "Effective Date", na.value = "grey50", guide = "legend", drop = "TRUE") +
  theme(axis.text.x = element_blank(),
        axis.text.y = element_blank(),
        axis.ticks = element_blank(),
        rect = element_blank(),
        axis.title.y=element_blank(), 
        axis.title.x=element_blank()) 

```

# State Policy Actions

In recent weeks, Governors across the US have issued executive orders requiring that businesses change or limit their in-person operations. In most states, restaurants are only permitted to operate take-out and/or delivery services. While some restaurants have opted to stay open and attempt to weather the storm with reduced operations, others have shut down entirely. This has resulted in mass layoffs in the food service industry across the country, contributing to the skyrocketing UI claims numbers. 

Further, in some states, Governors have called for all non-essential businesses to close. Many shops and malls, theaters and museums, gyms and yoga studios, and concert halls and clubs have been ordered to cease operations. While some businesses can scale up their e-commerce operations or survive on take-out orders alone, many are forced to lay off their workers. 

The timing of states' closure orders have varied, so we've put together some maps to show the timin

##Orders Affecting Business Operations and Closures

```{r, echo=FALSE, warning=FALSE, message=FALSE}

complete_map
takeout_map
```

We define partial closures as orders that prohibited restaurants from having patrons dine in. In many states, other provisions were included in these orders (e.g., limits on gathering sizes, requirements for bars/clubs to close). We use the switch to take-out only for consistency. 

We define complete closures as orders for non-essential businesses to close. States vary in their definitions of essential businesses, and some states also put stay at home or shelter in place orders. For consistency, we hone in specifically on the non-essential business closures. 

Both of these definitions are consistent with analyzing policy effects on UI claims and search activity -- as businesses close, layoffs increase. 


```{r, echo=FALSE, warning=FALSE, message=FALSE}

#Set up data for event studies
data_policy_states2 <- data_policy_states 
names(data_policy_states2)[names(data_policy_states2) == "state_abbr"] <- "location"
data_policy_states2 <- within(data_policy_states2, rm("notes", "region", "fips"))

policy_event_study <- left_join(data_states_short_combined, data_policy_states2, by = "location") 
policy_event_study <- subset(policy_event_study, date > as.Date("2020-03-01") )

policy_event_study$daystopartial<- difftime(policy_event_study$date, policy_event_study$partial , units = c("days"))
policy_event_study$daystocomplete<- difftime(policy_event_study$date, policy_event_study$complete , units = c("days"))

#Define event study pre and post length
es_start = -7
es_end = 4
es_length = 11

#Event study around partial closure policies
partial_es_data <-
  policy_event_study %>% 
  drop_na(partial) %>% 
  filter(daystopartial >= es_start & daystopartial <= es_end)

## This sets the baseline period to t-1, change by making ref = 8 for t0 or ref = 6 for t-2
partial_es_data <- within(partial_es_data, daystopartial <- relevel(as.factor(daystopartial), ref = 7))

partial_es <- plm(hits ~ as.factor(daystopartial), 
             data = partial_es_data, 
             index = "location", 
             effect = "individual",
             model = "within")

partial_coefs = as.data.frame(summary(partial_es)$coefficients[1:es_length])
colnames(coefs)[1] <- "coeffecients"
partial_coefs$timefrompartial <- es_start:(es_end-1)
partial_coefs$timefrompartial <- ifelse(partial_coefs$timefrompartial >=-1, partial_coefs$timefrompartial + 1, partial_coefs$timefrompartial)

#Plot the event study
partial_es_plot <- ggplot(data=coefs, aes(x=timefrompartial, y=coeffecients))+
  geom_line(,color = "light blue") + 
  geom_vline(xintercept = 0, color = "purple") +
  labs(y = "Change in Google Search Intensity",
       x = "Days from Partial Closure Order",
       title="Search Trends in Response to Partial Closures") +
  theme_classic(base_size=15) +
  scale_x_continuous(breaks = seq(-7, 4, by = 1))

#Event study around complete closure policies

complete_es_data <-
  policy_event_study %>% 
  drop_na(complete) %>% 
  filter(daystocomplete >= es_start & daystocomplete <= es_end)

## This sets the baseline period to t-1, change by making ref = 8 for t0 or ref = 6 for t-2
complete_es_data <- within(complete_es_data, daystocomplete <- relevel(as.factor(daystocomplete), ref = 7))

complete_es <- plm(hits ~ as.factor(daystocomplete), 
             data = partial_es_data, 
             index = "location", 
             effect = "individual",
             model = "within")

complete_coefs <- as.data.frame(summary(complete_es)$coefficients[1:es_length])
colnames(complete_coefs)[1] <- "coeffecients"
complete_coefs$timefromcomplete <- es_start:(es_end-1)
complete_coefs$timefromcomplete <- ifelse(complete_coefs$timefromcomplete >=-1, complete_coefs$timefromcomplete + 1, complete_coefs$timefromcomplete)

#Plot the event study
complete_es_plot <- ggplot(data=complete_coefs, aes(x=timefromcomplete, y=coeffecients))+
  geom_line(,color = "light blue") + 
  geom_vline(xintercept = 0, color = "blue") +
  labs(y = "Change in Google Search Intensity",
       x = "Days from Complete Closure Order",
       title="Search Trends in Response to Complete Closures") +
  theme_classic(base_size=15) +
  scale_x_continuous(breaks = seq(-7, 4, by = 1))



partial_es_plot
complete_es_plot

```



```{r, echo=FALSE, warning=FALSE, message=FALSE}

#Plot one state with both policies as an example (add daily UI first)

plotstate = "TX" #Change this to see another state

#First merge in daily UI data
  policy_event_study_withdailyui <- right_join(daily_UI_Claims, policy_event_study, by = c("location", "date"))
  policy_event_study_plotstate <- policy_event_study_withdailyui %>% 
    filter(location == plotstate)

#Plot daily trends data
dailygoogleplot_plotstate <- ggplot(data = policy_event_study_plotstate, aes(x=date, y=hits)) + 
  geom_line(,color = "light blue") + 
  geom_vline(aes(xintercept = mean(partial), color = "Partial"), show.guide = TRUE) + 
  geom_vline(aes(xintercept = mean(complete), color = "Complete"), show.guide = TRUE) +
  scale_color_manual(name = "Closure Orders", values = c(Partial = "blue", Complete = "purple")) +
  theme_classic(base_size=15) + 
  theme(legend.position = "bottom") +
  labs(x = "Time",
       y = "Google Search Trends", 
       title = paste("Google Search Trends Over Time in", plotstate))

#Plot daily UI claims with policies (this is pretty useless right now, because we don't have enough daily data)
dailyuiplot_plotstate <- ggplot(data = policy_event_study_plotstate, aes(x=date, y=ui_claims_daily)) + 
  geom_line(,color = "light blue") + 
  geom_vline(aes(xintercept = mean(partial), color = "Partial"), show.guide = TRUE) + 
  geom_vline(aes(xintercept = mean(complete), color = "Complete"), show.guide = TRUE) +
  scale_color_manual(name = "Closure Orders", values = c(Partial = "blue", Complete = "purple")) +
  theme_classic(base_size=15) + 
  theme(legend.position = "bottom") +
  labs(x = "Time",
       y = "Daily UI Claims", 
       title = paste("Daily UI Claims Over Time in", plotstate))

dailygoogleplot_plotstate
dailyuiplot_plotstate

```

```{r, echo=FALSE, warning=FALSE, message=FALSE}

#Now look at weekly search trends and UI data by week of policy adoption 

#First bring in weekly claims data prior to COVID 
weekly_UI_janthrumarch = as.data.frame(read_xlsx("data/UI_claims_jan1thrumarch21.xlsx"))
names(weekly_UI_janthrumarch)[names(weekly_UI_janthrumarch) == "State"] <- "state"
names(weekly_UI_janthrumarch)[names(weekly_UI_janthrumarch) == "Filed week ended"] <- "week"
names(weekly_UI_janthrumarch)[names(weekly_UI_janthrumarch) == "Initial Claims"] <- "claims"
weekly_UI_janthrumarch <- mutate_at(weekly_UI_janthrumarch, "week", funs(ymd)) %>%
  mutate(week = epiweek(week)) 
weekly_UI_janthrumarch <- subset(weekly_UI_janthrumarch, select = c("state", "week", "claims"))

weekly_UI_janthrumarch <- left_join(weekly_UI_janthrumarch, data_policy_states2[, c("state", "location")], by = "state")

#Clean data from week ending March 28 (4/2/20 news release)
week13ui <- subset(UI_Claims_March28_True, select = c("location", "advance_0322"))
week13ui$week <- 13
names(week13ui)[names(week13ui) == "advance_0322"] <- "claims"
week13ui <- left_join(week13ui, data_policy_states2[, c("state", "location")], by = "location")

#Merge together to get all weekly UI data available
weekly_UI_janthrumarch <- rbind(weekly_UI_janthrumarch, week13ui, by = "location")

#Merge with policy data at week-level
weekly_claims_policy <- left_join(weekly_UI_janthrumarch, data_policy_states2[, c("partial_week", "complete_week", "location")], by = "location")

weekly_claims_policy <- weekly_claims_policy %>%
    group_by(location) %>%
    mutate(week = as.numeric(week)) %>%
    arrange(location ,week) %>%
    mutate(claims = as.numeric(claims))  %>%
    mutate(claims_pchg = 100*(claims - dplyr::lag(claims))/dplyr::lag(claims)) %>%
    filter(week >=9) 

#There's really nothing interesting here. A few late-adopting states seem to have big increases in week 13, but I think this is more to do with technology issues (so claims were late). 

#ggplot(subset(weekly_claims_policy, complete_week == 13), aes(x = week, y = claims_pchg, color = state)) + geom_path()

#ggplot(subset(weekly_claims_policy, complete_week == 12), aes(x = week, y = claims_pchg, color = state)) + geom_path()

#ggplot(subset(weekly_claims_policy, partial_week == 12), aes(x = week, y = claims_pchg, color = state)) + geom_path()

#ggplot(subset(weekly_claims_policy, partial_week == 13), aes(x = week, y = claims_pchg, color = state)) + geom_path()

#ggplot(weekly_claims_policy, aes(x = week, y = claims_pchg, color = partial_week)) + geom_path()

weekly_claims_policy <- within(weekly_claims_policy, daystocomplete <- relevel(as.factor(daystocomplete), ref = 7))

complete_es <- plm(clsimd ~ as.factor(partial_week), 
             data = partial_es_data, 
             index = "location", 
             effect = "individual",
             model = "within")

```